Effect of quality-adjusted production function inputs

### 2015-05-17 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Added sentence and eqn about residuals.
Now using select.

<<Fitted_and_Residuals>>=
fitted_and_resid_data <- leaf_apply(models, class=c("CDEmodel", "cesEst", "LINEXmodel"), function(mod, id){
  df <- mod$data[ , c("Year", "iGDP", "Country")]
  # Trim fitted to be same length as df to eliminate problems with possible NAs at end of fitted
  df$fitted <- yhat(mod)[c(1:length(df$Year))]
  df$Residuals <- resid(mod)[c(1:length(df$Year))]
  # Parse the id to find out whether this is quality-adjusted data
  id_list <- strsplit(id, split = "[.]")[[1]]
  if (id_list[[2]] == "unadjusted"){
    df$flavor <- "Unadjusted"
  } else if (id_list[[2]] == "adjusted"){
    df$flavor <- "Quality-adjusted"
  } else {
    stop("Unknown adjustment.")
  }
  if (id_list[[3]] == "noE"){
    df$energy <- "Without energy"
  } else if (id_list[[3]] == "withE"){
    df$energy <- "With energy"
  } else {
    stop("Unknown energy.")
  }
  df$model <- id_list[[4]]
  df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
  return(df)  
}) %>% do.call(rbind, .)

@@

This section shows graphs of fits to historical data and residuals.

>>>>

<<Fitted_and_Residuals>>=
fitted_and_resid_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), function(mod, id){
  df <- select(mod$data, Year, iGDP, Country)
  # Trim fitted to be same length as df to eliminate problems with possible NAs at end of fitted
  df$fitted <- yhat(mod)[c(1:length(df$Year))]
  df$Residuals <- resid(mod)[c(1:length(df$Year))]
  # Parse the id to find out whether this is quality-adjusted data
  id_list <- strsplit(id, split = "[.]")[[1]]
  if (id_list[[2]] == "unadjusted"){
    df$flavor <- "Unadjusted"
  } else if (id_list[[2]] == "adjusted"){
    df$flavor <- "Quality-adjusted"
  } else {
    stop("Unknown adjustment.")
  }
  if (id_list[[3]] == "noE"){
    df$energy <- "Without energy"
  } else if (id_list[[3]] == "withE"){
    df$energy <- "With energy"
  } else {
    stop("Unknown energy.")
  }
  df$model <- id_list[[4]]
  df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
  return(df)  
}) %>% do.call(rbind, .)

@@

This section shows graphs of fits to historical data and residuals.
Because we fit in log-space, the residuals ($r_i$) are defined as
%
\begin{equation} \label{eq:log-residuals}
  r_i \equiv \ln(y_i) - \ln(\hat{y}_i) =\ln\left( \frac{y_i}{\hat{y}_i} \right), 
\end{equation}
%
where $r_i$ will be zero when there is agreement between 
historical~($y_i$) and fitted~($\hat{y}_i$) economic output.
